A Hierarchical Bayesian Framework for Inferring the Stellar Obliquity Distribution

### 2023-03-22 src/tex/ms.tex
[showyourwork] overleaf sync

@@

\begin{figure}[ht!]
    \script{graph.py}
    \includegraphics[width=\linewidth]{figures/graph.pdf}
    \caption{\edits{Need some edits: A probabilistic graphical model showing the conditional structure of our hierarchical Bayesian framework for inferring the stellar obliquity distribution of exoplanetary systems. The population model is parameterized by hyperparameters $\vb*{\beta}$, and it is constrained by the sky-projected stellar obliquity $\lambda_n$, orbital inclination $i_{{\rm orb}, n}$, and, if available, the stellar inclination $i_{\star, n}$ of each $n_{\rm th}$ individual system. Each system's stellar obliquity $\psi_n$ is inferred simultaneously based on these data. 
    Properties of the star other than its inclination, such as its radius and rotation period, are represented by $\gamma_{\star, n}$, and these can inform the constraint on $i_{\star, n}$, if available. 
    Obs$_{\star,n}$ contains all observed properties of the star with uncertainties, $\hat{\lambda}_n$ has the measured sky-projected stellar obliquity and its uncertainty, and $\hat{i}_{{\rm orb}, n}$ has measured orbital inclination and its uncertainty.}}
    \label{fig:graph}
\end{figure}

>>>>

In the $\{\lambda, i_\star\}$ coordinate system, where the $\vb{x'}$-axis is defined by the observer's line of sight, the stellar spin axis could be written as 
\begin{equation}
    \vb{n_\star}' = \cos{i_\star}\vu*{x}' + \sin{i_\star}\sin{\lambda}\vu*{y}' + \sin{i_\star}\cos{\lambda}\vu*{z}'
\end{equation}

To convert the stellar spin vector $\vb{n_\star}$ from $\vb{x,y,z}$ to $\vb{x',y',z'}$, we apply the rotation matrix to the vector by rotating the vector by $\pi/2 - i_{\rm orb}$ around the $\vb{y'}$-axis. 
\begin{equation}
      \vb{n_\star}' = \mqty[\sin{i_{\rm orb}} & 0 & \cos{i_{\rm orb}} \\ 0 & 1 & 0 \\ -\cos{i_{\rm orb}} & 0 & \sin{i_{\rm orb}}] \vb{n_\star}  
\end{equation}

Now we get $\vb{n_\star}'$ in the $\vb{x',y',z'}$ coordinate expressed by $\psi$, $\theta$, and $i_{\rm orb}$.
\begin{equation}
    \begin{split}
    \vb{n_\star}' = (\sin{\psi}\cos{\theta}\sin{i_{\rm orb}}+\cos{\psi}\cos{i_{\rm orb}})\vu*{x}' &\\
    + \sin{\psi}\sin{\theta}\vu*{y}'& \\
    + (-\sin{\psi}\cos{\theta}\cos{i_{\rm orb}}+\cos{\psi}\sin{i_{\rm orb}})\vu*{z}'&
    \end{split}
\end{equation}

Use the equation, we find the relation between $\lambda$ or $i_\star$ and $\psi$, $\theta$, and $i_{\rm orb}$.

First, comparing the $\vb{x'}$ terms, we find
\begin{equation}
    i_\star = \cos[-1](\sin{\psi}\cos{\theta}\sin{i_{\rm orb}}+\cos{\psi}\cos{i_{\rm orb}}).
\end{equation}

Dividing the $\vb{y'}$ term by the $\vb{z'}$ term, we get
\begin{equation}
    \lambda = \tan[-1](\frac{\sin{\psi}\sin{\theta}}{-\sin{\psi}\cos{\theta}\cos{i_{\rm orb}}+\cos{\psi}\sin{i_{\rm orb}}}).
\end{equation}

@@

\begin{figure}[ht!]
    \script{graph.py}
    \centering
    \includegraphics[width=0.8\linewidth]{figures/graph.pdf}
    \caption{\edits{Need some edits: A probabilistic graphical model showing the conditional structure of our hierarchical Bayesian framework for inferring the stellar obliquity distribution of exoplanetary systems. The population model is parameterized by hyperparameters $\vb*{\beta}$, and it is constrained by the sky-projected stellar obliquity $\lambda_n$, orbital inclination $i_{{\rm orb}, n}$, and, if available, the stellar inclination $i_{\star, n}$ of each $n_{\rm th}$ individual system. Each system's stellar obliquity $\psi_n$ is inferred simultaneously based on these data. 
    Properties of the star other than its inclination, such as its radius and rotation period, are represented by $\gamma_{\star, n}$, and these can inform the constraint on $i_{\star, n}$, if available. 
    Obs$_{\star,n}$ contains all observed properties of the star with uncertainties, $\hat{\lambda}_n$ has the measured sky-projected stellar obliquity and its uncertainty, and $\hat{i}_{{\rm orb}, n}$ has measured orbital inclination and its uncertainty.}}
    \label{fig:graph}
\end{figure}
